An example exploratory analysis script

### 2023-02-24 code/analysis_code/exploratory_analysis.qmd
part 2 work

## Save Graph
ggsave("time_v_hospitalization_pathogen_type.png", path = "results")

@@

## Save Graph
ggsave("pathogen_type_etiology_v_hospitalizations.png", path = "results")

@@

ggsave("bacterial_etiology_v_hospitalization_frequency.png", path = "results")

@@

saveRDS(state_v_hospitalization_training, file = "results/state_v_hospitalization_training.rds")

@@

ggsave("food_type_v_hospitalization.png", path = "results")

@@

## Save Graph
ggsave("time_v_illness_pathogen_type.png", path = "results")

@@

## Save Graph
ggsave("pathogen_type_etiology_v_illness.png", path = "results")

@@

ggsave("bacterial_etiology_v_outbreak_frequency.png", path = "results")

@@

saveRDS(state_v_illness_analysis, file = "results/state_v_illness_analysis.rds")

@@

ggsave("food_type_v_illness_frequency.png", path = "results")

>>>>

## Save Graph
image_path <- here("results")
ggsave("time_v_hospitalization_pathogen_type.png", path = image_path)

@@

## Save Graph
ggsave("pathogen_type_etiology_v_hospitalizations.png", path = image_path)

@@

ggsave("bacterial_etiology_v_hospitalization_frequency.png", path = image_path)

@@

## Save Table
table_path <- here("results", "state_v_hospitalization_training.rds")
saveRDS(state_v_hospitalization_training, file = table_path)

@@

ggsave("food_type_v_hospitalization.png", path = image_path)

@@

## Save Graph
ggsave("time_v_illness_pathogen_type.png", path = image_path)

@@

## Save Graph
ggsave("pathogen_type_etiology_v_illness.png", path = image_path)

@@

ggsave("bacterial_etiology_v_outbreak_frequency.png", path = image_path)

@@

saveRDS(state_v_illness_analysis, file = table_path)

@@

ggsave("food_type_v_illness_frequency.png", path = image_path)
